Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-04 analysis/paper/Rmd/hotspots-paper.Rmd
minor edits to paper

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 3, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
    self_contained: no
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
---

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 3, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
    self_contained: no
    keep_md: true
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
---
